\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2015-12-30 draft.tex
fix two typos identified by Ben Z.

When $\ga$ is exogenous, the optimal trade agreement tariff is the same under perfect external enforcement and self-enforcement because the change in enforcement conditions cannot affect the realization of $\ga$. We will see that moving from a static problem with external enforcement to a repeated-game problem with an enforcement constraint changes the lobby's decision problem. However, it does not alter the within-period costs and benefits and so in the case of endogenous political pressure we will see the same result that the optimal trade agreement tariff in invariant to the enforcement conditions.

@@

In this case, again the government does not have means to encourage any additional lobbying, but it can improve its situation by discouraging lobbying. By setting a tariff cap of zero---assuming the conditions for self enforcement outlined in Section~\ref{sec:selfweak} are met---the government can use the trade agreement to improve welfare by changing lobbying incentives and therefore the political pressure it encounters. The stark prediction that the best the government can do is by setting the trade agreement to zero would be softened in an environment such as that in Section~\ref{sec:escape2} where there are both endogenous and exogenous sources of political pressure or with a government welfare function that has a interior global maximum in $\ga$.

>>>>

When $\ga$ is exogenous, the optimal trade agreement tariff is the same under perfect external enforcement and self-enforcement because the change in enforcement conditions cannot affect the realization of $\ga$. We will see that moving from a static problem with external enforcement to a repeated-game problem with an enforcement constraint changes the lobby's decision problem. However, it does not alter the within-period costs and benefits and so in the case of endogenous political pressure we will see the same result that the optimal trade agreement tariff is invariant to the enforcement conditions.

@@

In this case, again the government does not have means to encourage any additional lobbying, but it can improve its situation by discouraging lobbying. By setting a tariff cap of zero---assuming the conditions for self enforcement outlined in Section~\ref{sec:selfweak} are met---the government can use the trade agreement to improve welfare by changing lobbying incentives and therefore the political pressure it encounters. The stark prediction that the best the government can do is by setting the trade agreement to zero would be softened in an environment such as that in Section~\ref{sec:escape2} where there are both endogenous and exogenous sources of political pressure or with a government welfare function that has an interior global maximum in $\ga$.
